Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-09-24 paper-v1.tex
Discussion: ref standard peer review

\subsection{A new community-driven standard?}
As Tennant points out \cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}). Recently, pre-print servers, such as arXiv and biorXiv, started integrating peer-review services into their platforms: \emph{PREreview} \footnote[20]{\emph{PREreview.}  \textsc{URL:} https://www.prereview.org}, \emph{PeerCommunityIn.} \footnote[21]{\emph{PeerCommunityIn} \textsc{URL:} https://peercommunityin.org}, \emph{Review Commons} \footnote[22]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review} \footnote[23]{\emph{PrePrint Review.} \textsc{URL:} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}. This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer-review platforms and justify their added value (\emph{ibidem}). In our proposal we also decoupled the peer-review process from the publishers giving it back to the scientific community and applying incentives from tokenomics. We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer-reviews: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[24]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}. \textsc{URL:} https://blog.frontiersin.org/2020/07/01/artificial-intelligence-peer-review-assistant-aira/.}) leaving to the reviewers the sole task of evaluating the content of a paper. Building smart-contracts for peer-reviews might accelerate this novel process of standardization. We hope that soon the value of peer review as a public good will be recognized by research funders and hiring committees.

>>>>

\subsection{A new community-driven standard?}
As Tennant points out \cite{Tennant2017-F1000R}, a change is already happening in the publishing industry, especially with new born publishers opening up the review process (\emph{BioMed Central}, \emph{ELife}, \emph{Frontiers}, \emph{PeerJ}, \emph{F1000 Research}). Recently, pre-print servers, such as arXiv and biorXiv, started integrating peer-review services into their platforms: \emph{PREreview} \footnote[20]{\emph{PREreview.}  \textsc{URL:} https://www.prereview.org}, \emph{PeerCommunityIn.} \footnote[21]{\emph{PeerCommunityIn} \textsc{URL:} https://peercommunityin.org}, \emph{Review Commons} \footnote[22]{\emph{Review Commons.} \textsc{URL:} https://www.reviewcommons.org}, \emph{PrePrint Review} \footnote[23]{\emph{PrePrint Review.} \textsc{URL:} https://elifesci.org/preprint-review} and the previously mentioned \emph{Peerage of Science}. This dissociation of initial scientific dissemination and scientific validation will force the publishing industry to adapt in order to keep up with the higher quality scientific process offered by those alternative peer-review platforms and justify their added value (\emph{ibidem}). In our proposal we also decoupled the peer-review process from the publishers giving it back to the scientific community and applying incentives from tokenomics. We foresee that the future will evolve towards community-driven peer-reviews: peer-reviews will be more and more independent from publishers \cite{DecoupJ}, and researchers will be the ones seeking the papers to review to build reputation within the community and not journals.
\newline Enlarging the pool of reviewers to potentially an entire scientific community and accelerating the whole process requires a standard for peer-reviews \cite{UPR}: for example some aspects might be taken over by AI assistants (such as the \emph{Artificial Intelligence Review Assistant (AIRA)}\footnote[24]{\emph{Artificial Intelligence to help meet global demand for high-quality, objective peer-review in publishing.} Posted on July 1, 2020 in \emph{Frontiers Announcements, Open Science and Peer Review}. \textsc{URL:} https://blog.frontiersin.org/2020/07/01/artificial-intelligence-peer-review-assistant-aira/.}) leaving to the reviewers the sole task of evaluating the content of a paper. Building smart-contracts for peer-reviews might accelerate this novel process of standardization. We hope that soon the value of peer review as a public good will be recognized by research funders and hiring committees.
